How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

In this paper, we have introduced a Cauchy formulation of the boundary integral equation method to simulate the fluid-mechanical erosion of many bodies in a Stokes flow. The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies with statistical analysis across an ensemble of different initializations. By linking the governing Stokes equation to Darcy's law, we are able to extract porous media properties, like permeability, resistivity, tortuosity, and anisotropy, as they evolve over time. By comparing the resistivity to the directly computed drag, we find that these porous-media properties can be extracted with high accuracy.

	The ratio of longitudinal to transverse permeability provides the main

>>>>

In this paper, we have presented a Cauchy formulation of the boundary integral equation method to simulate the fluid-mechanical erosion of many bodies in a Stokes flow. The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies and statistical analysis across an ensemble of different initializations. By linking the governing Stokes equation to Darcy's law, we are able to extract porous media properties, including permeability, resistivity, tortuosity, and anisotropy, as they evolve over time. Direct comparison of resistivity with the total drag force confirms such bulk properties are extracted with high accuracy.

	The ratio of longitudinal to transverse permeability provides our main diagnostic of medium anisotropy. Measurements indicate that the anisotropy grows substantially as a result of fluid mechanical erosion, reaching a peak of roughly six in most simulations, before the bodies completely vanish and return the system to an isotropic state. The anisotropy can be further decomposed into a configurational component, due only to the relative positions of bodies, and a shape component, due to the detailed geometry of each body. Statistical analysis across a large number of simulations reveals that if the number of bodies is sufficiently large, $M \ge 60$m, the configurational anisotropy surges near the final stages of erosion and surpasses the shape anisotropy as the primary contribution. This surge in configurational anisotropy is associated with the formation of visual channels that transmit a large portion of the flow. The tortuosity provides a second metric and also reveals strong anisotropy to develop across all simulations.
%though this metric shows less signal in the configurational contribution.
